\begin{thebibliography}{5}
\bibitem{SPP}
J. Kim, S. H. Pugsley, P. V. Gratz, A. L. N. Reddy, C. Wilkerson and Z. Chishti. Path Confidence-based Lookahead Prefetching. In {\it Proceedings of the 49th Annual IEEE/ACM International Symposium on Microarchitecture (MICRO)\/}, Taipei, 2016, pp. 1--12, doi: 10.1109/MICRO.2016.7783763.
\bibitem{Perceptron filtering}
Eshan Bhatia, Gino Chacon, Seth Pugsley, Elvira Teran, Paul V. Gratz, and Daniel A. Jiménez. Perceptron-based Prefetch Filtering. In {\it Proceedings of the 46th International Symposium on Computer Architecture (ISCA ’19)\/}, 2019. DOI:https://doi.org/10.1145/3307650.3322207


\bibitem{Kill The Program Counter}
Jinchun Kim, Elvira Teran, Paul V. Gratz, Daniel A. Jiménez, Seth H. Pugsley, and Chris Wilkerson. Kill the Program Counter: Reconstructing Program Behavior in the Processor Cache Hierarchy. In {\it Proceedings of the Twenty-Second International Conference on Architectural Support for Programming Languages and Operating Systems (ASPLOS ’17)\/}, 2017. DOI:https://doi.org/10.1145/3037697.3037701
\bibitem{Long-range prefetching}
Jamison D. Collins, Hong Wang, Dean M. Tullsen, Christopher Hughes, Yong-Fong Lee, Dan Lavery, and John P. Shen. 2001. Speculative precomputation: long-range prefetching of delinquent loads. In Proceedings of the 28th annual international symposium on Computer architecture (ISCA ’01). Association for Computing Machinery, New York, NY, USA, 14–25. DOI:https://doi.org/10.1145/379240.379248

\bibitem{Dynamic speculative precomputation}

Jamison D. Collins, Dean M. Tullsen, Hong Wang, and John P. Shen. 2001. Dynamic speculative precomputation. In Proceedings of the 34th annual ACM/IEEE international symposium on Microarchitecture (MICRO 34). IEEE Computer Society, USA, 306–317.


\bibitem{performance oriented prefetching}
R. Manikantan and R. Govindarajan. 2008. Focused prefetching: performance oriented prefetching based on commit stalls. In Proceedings of the 22nd annual international conference on Supercomputing (ICS ’08). Association for Computing Machinery, New York, NY, USA, 339–348. DOI:https://doi.org/10.1145/1375527.1375576
\bibitem{Survey of Recent Prefetching Techniques}
Sparsh Mittal. A Survey of Recent Prefetching Techniques for Processor Caches. In {\it ACM Computing Surveys\/}, {\bf 49}(2): Article 35, November 2016, 35 pages. DOI:https://doi.org/10.1145/2907071

\bibitem{Dynamic branch prediction with perceptrons}
D. A. Jimenez and C. Lin. Dynamic Branch Prediction with Perceptrons. In {\it Proceedings of the Seventh International Symposium on High-Performance Computer Architecture\/}, Monterrey, Nuevo Leon, Mexico, 2001, pp. 197--206, doi: 10.1109/HPCA.2001.903263.
\bibitem{Data Cache Prefetching Using a Global History Buffer}
K. J. Nesbit and J. E. Smith. Data Cache Prefetching Using a Global History Buffer. In {\it Proceedings of the 10th International Symposium on High Performance Computer Architecture (HPCA'04)\/}, Madrid, Spain, 2004. doi: 10.1109/HPCA.2004.10030.

\bibitem{Feedback Directed Prefetching}
S. Srinath, O. Mutlu, H. Kim and Y. N. Patt. Feedback Directed Prefetching: Improving the Performance and Bandwidth-Efficiency of Hardware Prefetchers. In {\it Proceedings of the 13th IEEE International Symposium on High Performance Computer Architecture\/}, Scottsdale, AZ, 2007, pp. 63--74, doi: 10.1109/HPCA.2007.346185.

\bibitem{
Mitigating Prefetcher-Caused Pollution Using Informed Caching Policies for Prefetched Blocks}
Vivek Seshadri, Samihan Yedkar, Hongyi Xin, Onur Mutlu, Phillip B. Gibbons, Michael A. Kozuch, and Todd C. Mowry. Mitigating Prefetcher-Caused Pollution Using Informed Caching Policies for Prefetched Blocks. In {\it ACM Transactions on Architecture and Code Optimization\/}, {\bf 11}(4): Article 51, January 2015, 22 pages. DOI:https://doi.org/10.1145/2677956

\bibitem{Superscalar}
J. E. Smith and G. S. Sohi. The Microarchitecture of Superscalar Processors. In {\it Proceedings of the IEEE\/}, {\bf 83}(12): 1609--1624, Dec. 1995, doi: 10.1109/5.476078.

\bibitem{IPCP}
S. Pakalapati and B. Panda. Bouquet of Instruction Pointers: Instruction Pointer Classifier-based Spatial Hardware Prefetching.
In {\it Proceedings of the 47th ACM/IEEE Annual International Symposium on Computer Architecture\/}, pp. 118--131, May/June 2020.

\bibitem{Champsim}
Github Repository of the ChampSim Simulator.  https://github.com/ChampSim/ChampSim

\bibitem{SPEC2017}
SPEC(Standard Performance Evaluation Corporation) benchmark's Home Page. https://www.spec.org/cpu2017/

\bibitem{git}
 Github Repository for the Thesis code.   https://github.com/jatindev2016/ChampSim-master-jatin-thesis

\end{thebibliography}